\newpage
\addcontentsline{toc}{section}{References}
\bibliographystyle{plain}
\bibliography{references}
\begin{thebibliography}{9}
\bibitem{gps} 
What is GPS?,
\\\texttt{http://www.loc.gov/rr/scitech/mysteries/global.html}

\bibitem{gps-vs-glonass}
GPS vs GLONASS: Which is Best for Tracking Applications?,
\\\texttt{https://www.semiconductorstore.com/blog/2015/GPS-vs-GLONASS
-Which-is-Best-for-Tracking-Applications/810}

\bibitem{glonass-gps-1}
Benefits of Combined GPS/GLONASS with Low-Cost MEMS IMUs for Vehicular Urban Navigation,
\\\texttt{\url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3355462/}}

\bibitem{glonass-gps-2}
GLONASS significantly benefits GPS,
\\\texttt{\url{http://www.oxts.com/glonass-significantly-benefits-gps/}}

\bibitem{russian-monitoring-system}
Russian System of Differentional Correction and Monitoring
\\\texttt{\url{http://www.sdcm.ru/index_eng.html}}

\bibitem{gps-gov}
GPS: The Global Positioning System
\\\texttt{\url{https://gps.gov}}

\bibitem{gps-indoor-precision}
Z. Horvath, H. Horvath (2014): 
\textit{The Measurement Preciseness of the GPS Built in Smartphones and Tablets,} International Journal on Electronics and Communication Technology, issue 1, pp 17-19

\bibitem{ips-definition}
Curran, Kevin; Furey, Eoghan; Lunney, Tom; Santos, Jose; Woods, Derek; McCaughey, Aiden (2011). 
\textit{An Evaluation of Indoor Location Determination Technologies.}
Journal of Location Based Services. 5 (2): 61–78.

\bibitem{triliteration-methods}
Triliteration
\\\texttt{\url{https://www.britannica.com/science/trilateration}}

\bibitem{ar-definition}
Schuettel, Patrick (2017). 
\textit{The Concise Fintech Compendium.} Fribourg: School of Management Fribourg/Switzerland.

\bibitem{ar-definition-2}
Rosenberg, L.B. (1992). 
\textit{The Use of Virtual Fixtures As Perceptual Overlays to Enhance Operator Performance in Remote Environments.}
Technical Report AL-TR-0089, USAF Armstrong Laboratory, Wright-Patterson AFB OH, 1992.

\bibitem{ar-nav-1}
Couts, Andrew. 
\textit{New augmented reality system shows 3D GPS navigation through your windshield.} Digital Trens, 27 October 2011

\bibitem{ar-nav-2}
Griggs, Brandon. \textit{Augmented-reality' windshields and the future of driving CNN Tech.} 13 January 2012.

\bibitem{nasa-ar-nav}
Delgado, F., Abernathy, M., White J., and Lowrey, B. 
\textit{Real-Time 3-D Flight Guidance with Terrain for the X-38,SPIE Enhanced and Synthetic Vision.} 
1999, Orlando Florida, April 1999, Proceedings of the SPIE Vol. 3691, pages 149–156

\bibitem{triliteration-image}
Positioning and triliteration,
\\\texttt{\url{https://www.alanzucconi.com/2017/03/13/positioning-and-trilateration/}}

\bibitem{cormen}
Thomas H. Cormen, Charles E. Leiserson, Ronald L. Rivest, and Clifford Stein. 2009. 
\textit{Introduction to Algorithms, Third Edition (3rd ed.).} 
The MIT Press.

\bibitem{three-tier}
Three Tier Architecture
\\\texttt{\url{https://www.techopedia.com/definition/24649/three-tier-architecture}}

\bibitem{wifi-map}
Shin, H., Chon, Y., Cha, H. (2012).
\textit{Unsupervised construction of an indoor floor plan using a smartphone.}
IEEE Transactions on Systems, Man and Cybernetics Part C: Applications and Reviews, 42(6), 889–898. \\\texttt{\url{https://doi.org/10.1109/TSMCC.2011.2169403}}

\bibitem{SLAM}
SLAM,
\\\texttt{\url{https://en.wikipedia.org/wiki/Simultaneous_localization_and_mapping}}

\bibitem{SLAM-auto}
Mountney, P.; et al. (Stoyanov, D.; Davison, A.; Yang, G-Z.) (2006). 
\textit{"Simultaneous Stereoscope Localization and Soft-Tissue Mapping for Minimal Invasive Surgery".}
MICCAI. Lecture Notes in Computer Science. 1: 347–354.

\bibitem{ips-survey-paper}
Koyuncu, H., \& Yang, S. H. (2010). 
\textit{A Survey of Indoor Positioning and Object Locating Systems.}
International Journal of Computer Science and Network Security (IJCSNS ’10), 10(5), 121–128.

\bibitem{apple-indoor-survey}
Apple’s survey app helps venues easily create indoor maps,
\\\texttt{\url{https://www.theverge.com/2015/11/2/9657304/apple-indoor-mapping-survey-app}}

\bibitem{iOS}
iOS,
\\\texttt{\url{https://en.wikipedia.org/wiki/IOS}}

\bibitem{swift}
Swift,
\\\texttt{\url{https://swift.org/about/}}

\bibitem{vapor}
Vapor,
\\\texttt{\url{https://vapor.codes}}

\bibitem{python}
Python,
\\\texttt{\url{https://www.python.org/about/}}

\bibitem{flask}
Flask,
\\\texttt{\url{http://flask.pocoo.org}}

\bibitem{linux}
Linux,
\\\texttt{\url{https://en.wikipedia.org/wiki/Linux}}

\bibitem{arkit}
ARKit,
\\\texttt{\url{https://developer.apple.com/arkit/}}

\bibitem{postgresql}
PostgreSQL,
\\\texttt{\url{https://www.postgresql.org/about/}}

\bibitem{compass}
King, T., Kopf, S., Haenselmann, T., Lubberger, C., \& Effelsberg, W. (2006). 
\textit{Compass.}
Proceedings of the 1st International Workshop on Wireless Network Testbeds, Experimental Evaluation \& Characterization  - WiNTECH ’06, (January), 34. \\\texttt{\url{https://doi.org/10.1145/1160987.1160995}}

\bibitem{wifi-explore-paper}
Evennou, F., Marx, F. (2006). 
\textit{Advanced integration of WiFi and inertial navigation systems for indoor mobile positioning.}
Eurasip Journal on Applied Signal Processing, 2006, 1–11. 
\\\texttt{\url{https://doi.org/10.1155/ASP/2006/86706}}

\end{thebibliography}